---
title: "p8015_hw6_ax2173"
output: github_document
---

```{r}  
library(tidyverse)
library(modelr)
library(viridis)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = '90%'
)

theme_set(theme_classic() + theme(legend.position = 'bottom'))

options(
  ggplot2.continous.colour = 'viridis_d',
  ggplot2.continous.fill = 'viridis_d'
)

scalr_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Problem 1


## Problem 2

Import the data, and do some initial data manipulation, described as following:
* Create a city_state variable
* create a binary variable indicating whether the homicide is solved. (1 represents solved, 0 represents unsolved)
* Omit several cities
* Limit analysis those for whom victim_race is white or black
* change the type of victim_age to numeric

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, ', ',state),
    whether_solve = ifelse(str_detect(disposition, 'Close'), 1, 0)
  ) %>% 
  filter(
    !city_state %in% c('Dallas, TX', 'Phoenix, AZ','Kansas City, MO','Tulsa, AL'),
    victim_race %in% c('White','Black')
    ) %>% 
  mutate(victim_age = as.numeric(victim_age))
```



## Problem 3

