---
title: "p8015_hw6_ax2173"
output: github_document
---

```{r}  
library(tidyverse)
library(modelr)
library(viridis)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = '90%'
)

theme_set(theme_classic() + theme(legend.position = 'bottom'))

options(
  ggplot2.continous.colour = 'viridis_d',
  ggplot2.continous.fill = 'viridis_d'
)

scalr_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Problem 1


## Problem 2

Import the data, and do some initial data manipulations, described as following:

* Create a city_state variable
* Create a binary variable indicating whether the homicide is solved. (1 represents solved, 0 represents unsolved)
* Omit several cities
* Limit analysis those for whom victim_race is white or black
* Change the type of victim_age to numeric

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, ', ',state),
    whether_solve = ifelse(str_detect(disposition, 'Close'), 1, 0)
  ) %>% 
  select(-city, -state, -disposition) %>% 
  filter(
    !city_state %in% c('Dallas, TX', 'Phoenix, AZ','Kansas City, MO','Tulsa, AL'),
    victim_race %in% c('White','Black')
    ) %>% 
  filter(victim_age != 'Unknown') %>% 
  mutate(victim_age = as.numeric(victim_age))
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object, and apply the broom::tidy to this object.

```{r}
homicide_Bal_df = 
  homicide_df %>% 
  filter(city_state == 'Baltimore, MD') 

Bal_glm = 
  glm(whether_solve ~ victim_age + victim_sex + victim_race, family = binomial(link = logit), data = homicide_Bal_df) %>% 
  broom::tidy()
```

As for solving homicides comparing male victims to female victims keeping all other variables fixed, we can get these two things:

 * The estimated odds ratio is `r round(Bal_glm$estimate[[3]],3)`
 * The 95% confidence interval is (`r round(Bal_glm$estimate[[3]]-1.96*Bal_glm$std.error[[3]],3)`,`r round(Bal_glm$estimate[[3]]+1.96*Bal_glm$std.error[[3]],3)`)


Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. 

```{r}
homicide_df_models = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = purrr::map(.x = data, ~glm(whether_solve ~ victim_age + victim_sex + victim_race, family = binomial(link = logit), data = .x)),
    result = purrr::map(models, broom::tidy)
    ) %>% 
  select(-data, -models) %>% 
  unnest(result) %>% 
  filter(term == 'victim_sexMale') %>% 
  mutate(
    CI_lowerbond = estimate - 1.96 * std.error,
    CI_upperbond = estimate + 1.96 * std.error,
  ) %>% 
  select(city_state, estimate, CI_lowerbond, CI_upperbond) 

homicide_df_models %>% knitr::kable(digits = 3)
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r fig.width=9, fig.height=6}
homicide_df_models %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(city_state, estimate, color = city_state)) +
  geom_linerange(aes(ymin = CI_lowerbond, ymax = CI_upperbond)) +
  geom_errorbar(aes(ymin = CI_lowerbond, ymax = CI_upperbond), width = 0.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5, vjust = 0.5)) +
  theme(legend.position = 'none') +
  labs(
    title = 'The Estimated ORs and CIs for Each City',
    x = 'Cities and states',
    y = 'Estimated ORs and CIs',
    caption = 'UNI: ax2173'
  )
```

Comments on this plot:

* The lowest estimated OR goes to New York, NY
* The highest estimated OR goes to Fresno, CA
* The widest CI goes to Long Beach, CA
* The narrowest CI goes to Chicago, IL

## Problem 3

